---
title: "madr"
author: "Heather Savoy"
date: "`r format(Sys.time(), '%a %b %d %Y')`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{madr}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

The `madr` package is intended to handle the post-processing of projects created by MAD#, the software implmentation of the Method of Anchored distributions (see our [Codeplex site](http://www.mad.codeplex.com)). 

However, the package is in early development and as such only has the following features:

- Reading the MAD# databases into a `MADproject` S4 class object
- Calculating non-parametric likelihood values using the `np` package 
- Calculating posterior distributions
- Generating plots for the observations, realizations, and posteriors

while making the following assumptions:

- There is only one measurement location (more that one can be read into the `MADproject` object but will not be handled for analysis and plotting).
- There is a single random parameter and its prior is a discrete uniform distribution.
- The inversion data consist of timesteps from the single measurement location's time series.

## Vignette Info

This vingnette will step through an example using the data `pumping`

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output:
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side.

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
