---
title: "madr"
author: "Heather Savoy"
date: "`r format(Sys.time(), '%a %b %d %Y')`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{madr}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


The `madr` package is intended to handle the post-processing of projects created by MAD#, the software implmentation of the Method of Anchored distributions (see our [Codeplex site](http://www.codeplex.com/mad)). 

However, the package is in early development and as such only has the following features:

- Reading the MAD# databases into a `MADproject` S4 class object
- Calculating non-parametric likelihood values using the `np` package 
- Testing convergence of likelihood values as a function of the number of realizations
- Calculating posterior distributions
- Generating plots for the observations, realizations, and posteriors

while making the following assumptions:

- There is only one measurement location (more that one can be read into the `MADproject` object but will not be handled for analysis and plotting).
- There is a single random parameter and its prior is a discrete uniform distribution.
- The inversion data consist of timesteps from the single measurement location's time series, a parameter-less function (e.g. `min`) of that time series, or a function to be fitted to the time series (e.g. `matern`). 

## Vignette Info

This vingnette will step through an example of applying `madr` using the dataset `pumping` which contains results from a MAD# project pertaining to characterizing an aquifer's mean natural-log hydraulic conductivity by using a time series of drawdown (change in hydraulic head) at a monitoring well in the field as inversion data. The `MADproject` object has slots `projectname`, `numSamples`, `observations`, and `realizations` filled. Normally, the function `readMAD` would be used to fill in the object from databases produced by MAD#, but this has done already for `pumping` for a more portable example. This also helps show that the use of MAD# is not entirely necessary: you can fill in a `MADproject` object with data from another application and still apply the MAD analysis. 
```{r, message=FALSE, echo=FALSE}
library(np)
```
```{r}
library(madr)
data("pumping")
```

## Viewing Data
The `plot` function can be used to view different data from the `MADproject` object. Pass the object as the first argument followed by

- nothing: yields all available plots given data
- `"observations"`: yields a plot of the observation as a function of time step.
- `"realizations"`: yields a plot of the samples' realizations as a polygon representing the interquartile ranges of the realization values as a function of the time steps. Only works if `@numSamples` is less than five. The observations is also plotted for comparison.
- `"posterior"`: yields a barplot of the posterior distribution for the samples. 

Below is an example of requesting to plot the realizations for the `pumping` dataset.
```{r, fig.width=7.2, fig.height=4 }
plot(pumping, "realizations")
```
 
## Applying MAD
The `madr` package can take this information and calculate the posterior of the random parameter in question based on requested inversion data. Below, the 100th time step is used as the inversion data, then the posterior is calculated and plotted (again, using the `plot` function).

```{r, results='hide'}
pumping <- calcLikelihood(pumping, list(timesteps=100))
pumping <- calcPosterior(pumping)
```
```{r, fig.width=7.2, fig.height=4}
plot(pumping, "posteriors")
```

## Applying MAD with Dimension Reduction
The `madr` package can take this information and calculate the posterior of the random parameter in question based on requested inversion data. Below, the 100th time step is used as the inversion data, then the posterior is calculated and plotted (again, using the `plot` function).

```{r, results='hide'}
pumping.min <- reduceData(pumping, min)
pumping.min <- calcLikelihood(pumping.min)
pumping.min <- calcPosterior(pumping.min)
```
```{r, fig.width=7.2, fig.height=4}
plot(pumping.min, "posteriors")
```

```{r, results='hide'}
pumping.matern <- reduceData(pumping, matern, init.matern)
```
```{r, fig.width=7.2, fig.height=8}
plot(pumping.matern, "realizations")
```
```{r, results='hide'}
pumping.matern <- calcLikelihood(pumping.matern)
pumping.matern <- calcPosterior(pumping.matern)
```
```{r, fig.width=7.2, fig.height=4}
plot(pumping.matern, "posteriors")
```

## Convergence testing
In order to assess the convergence of the likelihood values, you can call the 
`test_convergence` function that will take a MADproject object and calculate
likelihood values for a range of realization counts.
```{r, fig.width=7.2, fig.height=4, message=FALSE, results='hide'}
test_convergence(pumping.matern, samples=2:4)
```

## Coming Soon
Here are additional features that are planned for near-future development:

- More than one measurement location
- Dimension reduction techniques so more than just time steps can be used for inversion
- Continuous priors/posteriors
- Multiple random parameters
